### 2025-01-29 paper/preprint/paper.tex
nice
ready to start writing this up

\usepackage{arxiv}
\usepackage{orcidlink}
\usepackage{amsmath}
\usepackage[T1]{fontenc}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother

@@

\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdfkeywords={Counterfactual Explanations, Explainable AI},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\newcommand{\runninghead}{A Preprint }
\renewcommand{\runninghead}{A Preprint }
\def\asep{\\\\\\ } % default: all authors on same column
\author{}
\date{}
\begin{document}
{\bfseries \emph Keywords}
\def\sep{\textbullet\ }
Counterfactual Explanations \sep 
Explainable AI

\section{Abstract}\label{abstract}

Counterfactual Explanations (CE) have emerged as a popular method to
explain the predictions made by opaque machine learning models in a
post-hoc fashion. We propose a novel approach that leverages
counterfactuals during the training phase of models.

@@

\subsubsection{Generator Params}\label{generator-params}

>>>>

\usepackage{arxiv}
\usepackage{orcidlink}
\usepackage{amsmath}
\usepackage[T1]{fontenc}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\usepackage{amsthm}
\theoremstyle{definition}
\newtheorem{exercise}{Parameters}[section]
\theoremstyle{remark}
\AtBeginDocument{\renewcommand*{\proofname}{Proof}}
\newtheorem*{remark}{Remark}
\newtheorem*{solution}{Solution}
\newtheorem{refremark}{Remark}[section]
\newtheorem{refsolution}{Solution}[section]
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother

@@

\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Counterfactual Training: Teaching Models Plausible and Actionable Explanations},
  pdfauthor={Patrick Altmeyer; Arie van Deursen; Cynthia C. S. Liem},
  pdfkeywords={Counterfactual Explanations, Explainable AI},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\usepackage{lineno}
\linenumbers
\newcommand{\runninghead}{A Preprint }
\renewcommand{\runninghead}{Counterfactual Training (A Preprint) }
\title{Counterfactual Training: Teaching Models Plausible and Actionable
Explanations}
\def\asep{\\\\\\ } % default: all authors on same column
\def\asep{\And }
\author{\textbf{Patrick
Altmeyer}~\orcidlink{0000-0003-4726-8613}\\Faculty of Electrical
Engineering, Mathematics and Computer Science\\Delft University of
Technology\\\\\href{mailto:p.altmeyer@tudelft.nl}{p.altmeyer@tudelft.nl}\asep\textbf{Arie
van Deursen}\\Faculty of Electrical Engineering, Mathematics and
Computer Science\\Delft University of Technology\\\\\asep\textbf{Cynthia
C. S. Liem}\\Faculty of Electrical Engineering, Mathematics and Computer
Science\\Delft University of Technology\\\\}
\date{}
\begin{document}
\maketitle
\begin{abstract}
Counterfactual Explanations (CE) have emerged as a popular method to
explain the predictions made by opaque machine learning models in a
post-hoc fashion. We propose a novel approach that leverages
counterfactuals during the training phase of models.
\end{abstract}
{\bfseries \emph Keywords}
\def\sep{\textbullet\ }
Counterfactual Explanations \sep 
Explainable AI

@@

\subsubsection{Generator Parameters}\label{generator-parameters}

The hyperparameter choices are shown in
Parameters~\ref{exr-gen-params-first-run}:

\begin{exercise}[Parameters]\protect\hypertarget{exr-gen-params-first-run}{}\label{exr-gen-params-first-run}

~

\begin{itemize}
\tightlist
\item
  \textbf{generator\_params}:

  \begin{itemize}
  \tightlist
  \item
    \textbf{lambda\_cost}: 0.0, 0.001, 0.1
  \item
    \textbf{lambda\_energy}: 0.01, 0.05, 0.1, 0.5, 1.0, 5.0, 10.0, 15.0
  \item
    \textbf{lr}: 1.0
  \item
    \textbf{maxiter}: 20, 50, 100
  \item
    \textbf{opt}: sgd
  \end{itemize}
\item
  \textbf{generator\_type}: ecco, generic, omni, revise
\item
  \textbf{training\_params}:

  \begin{itemize}
  \tightlist
  \item
    \textbf{objective}: full, vanilla
  \end{itemize}
\end{itemize}

\end{exercise}

### 2025-01-29 paper/sections/appendix.qmd
nice
ready to start writing this up

### Generator Params

```{julia}
dict = CTExperiments.from_toml(joinpath(config_dir,"gen_params.toml")) 
```

>>>>

### Generator Parameters

The hyperparameter choices are shown in @exr-gen-params-first-run:

::: {#exr-gen-params-first-run}

## Parameters

```{julia}
#| output: asis
dict = CTExperiments.from_toml(joinpath(config_dir,"gen_params.toml")) 
println(CTExperiments.dict_to_quarto_markdown(dict))
```
